Compositionality and Modularity Together at Last!

### 2015-05-22 dAlg/mrm.tex
Refactoring early parts of the paper
Small changes
Section 4.1, 4.2
Section 4.3, 4.4 (multiple & dependent interpretation)
Context sensitive interpretation (part)
Clean up for type-class and record

@@

\title{Expressive, Modular and Compositional Embedded DSLs}
\subtitle{(Functional Pearl)}

\author[P. Boya and B. C. d. S. Oliveira]
        {PENG BOYA and BRUNO C. d. S. OLIVEIRA\\
         The University of Hong Kong, Hong Kong\\
         \email{bruno@cs.hku.hk}}\bruno{Fix author info later!}

@@

\begin{abstract}
Compositionality is a desirable characteristic for the semantics of
DSLs. In functional programming folds can be used to enforce
compositionality. However folds make certain compositional
interpretations hard to express modularly. This pearl presents a
simple technique that allows non-trivial, but compositional
interpretations of DSLs to be expressed in a fully modular way
using folds.

\begin{comment}

This paper presents composable algebra with dependencies: a new approach to compose 
algebras together to allow dependent interpretations with {\em fold}. 
For a given datatype represented by two-level-types\cite{sheard04}, if one of its 
interpretations depends on a second one, we compose the algebra correponding 
to the first interpretation with the one corresponding to the second, and use the 
composed algebra with {\em fold} to evaluate the expression. We present our approach 
on top of the domain specific language for parallel prefix circuits.

\end{comment}

\end{abstract}

@@

@@

\input{sections/Overview}

\input{sections/ComposableAlg}

@@

\input{sections/Extensibility}

\section{Other representations of algebra}
\label{sec: other-alg}

Apart from {\em two-level-types}, there are other ways to represent and evaluate
the DSL for parallel prefix circuits. In this section, we will show two other 
representations, and how they can be used to allow dependent interpretations.

@@

\input{sections/RelatedWork}

@@

>>>>

\newcommand\emma[1]{\textcolor{magenta}{[EM: #1]}}

@@

\title{Compositionality and Modularity Together at Last!}
\subtitle{(Functional Pearl)}

\author[B. Peng and B. C. d. S. Oliveira]
        {BOYA PENG and BRUNO C. d. S. OLIVEIRA\\
         The University of Hong Kong, Hong Kong\\
         \email{bruno@cs.hku.hk}}

@@

\begin{abstract}
Compositionality is a desirable characteristic for the semantics of
DSLs. In functional programming folds can be used to enforce
compositionality. However folds make certain compositional
interpretations hard to express modularly. This pearl presents a
simple technique that allows non-trivial, but compositional
interpretations of DSLs to be expressed in a fully modular way
using folds.
\end{abstract}

@@

\input{sections/Technique}

@@

%\input{sections/Overview}

\input{sections/MultipleAlg}

@@

\input{sections/Context}

%\input{sections/Extensibility}

@@

%\input{sections/RelatedWork}

@@

\bibitem{blelloch90}  
  Blelloch, Guy E..
  Prefix sums and their applications
  \emph{Technical Report}
  1990
